---
title: "Main_project_file"
format: html
editor: source
---

```{r}
library(tidyverse)
library(ggplot2)
library(knitr)
```

## Importing data into R

```{r}
taylor_album_songs <- read_csv("/Users/donyabehroozi/Desktop/stat365/stat-365/data/taylor_album_songs.csv")
taylor_ratings <- read_csv("/Users/donyabehroozi/Desktop/stat365/stat-365/data/taylor_albums.csv")
```

## Merging data sets together

```{r}
taylor_albums_joined <- taylor_album_songs |>
  left_join(taylor_ratings, by = c("album_name", ep = "ep", album_release = "album_release"))

head(taylor_albums_joined)
```

# Linear regression analysis (danceability vs. user scores)

```{r}
taylor.fit1=lm(danceability~user_score, data = taylor_albums_joined)

taylor_albums_joined |>
  ggplot(aes(x = user_score, y = danceability)) +
  geom_point(size = 2, shape = 1) +
  geom_smooth(method = "lm") +
  labs(title = "Scatter Plot of Danceability vs. User Score", x = "User Score", y = " ", subtitle = "Danceability") +
  theme_light() +
  theme(plot.title = element_text(face = "bold")) +
  annotate(geom = "label",
           x = 8.75,
           y = 0.7,
           label = "Regression line") +
  annotate(geom = "segment",
           x = 8.75,
           y = 0.68,
           xend = 8.75,
           yend = 0.61,
           arrow = arrow(length = unit(0.15, "inches"))) +
  scale_y_continuous(breaks = c(0.2, 0.4, 0.6,  0.8, 1.0))

```

# Hypotheses

$H_0$: Audience rating is not linearly associated with danceability score.

$H_A$: Audience rating is linearly associated with danceability score.

# Checking simple linear regression assumptions

```{r}
par(mfrow=c(1,3))
plot(resid(taylor.fit1)~fitted(taylor.fit1), xlab='Fitted', ylab='Residuals');abline(h=0,lty=2)
qqnorm(resid(taylor.fit1),ylab='Residuals'); qqline(resid(taylor.fit1),lty=2)
hist(resid(taylor.fit1),main="", xlab="Residuals",col='lightblue')
```

# Results and conclusion

```{r}
summary(taylor.fit1)
```
```{r}
confint(taylor.fit1, level = 0.95)
```


# Linear regression analysis (danceability vs. metacritic scores)

```{r}
taylor.fit2=lm(danceability~metacritic_score, data = taylor_albums_joined)

taylor_albums_joined |>
  ggplot(aes(x = metacritic_score, y = danceability)) +
  geom_point(size = 2, shape = 1) +
  geom_smooth(method = "lm") +
  labs(title = "Scatter Plot of Danceability vs. Metacritic Score", x = "Metacritic Score", y = " ", subtitle = "Danceability") +
  theme_light() +
  theme(plot.title = element_text(face = "bold")) +
  annotate(geom = "label",
           x = 72.5,
           y = 0.45,
           label = "Regression line")  +
  annotate(geom = "segment",
           x = 72.5,
           y = 0.48,
           xend = 72.5,
           yend = 0.56,
           arrow = arrow(length = unit(0.15, "inches"))) +
  scale_y_continuous(breaks = c(0.2, 0.4, 0.6,  0.8, 1.0))
```


# Hypotheses

$H_0$: Metacritic rating is not linearly associated with danceability score.

$H_A$: Metacritic rating is linearly associated with danceability score.

# Checking simple linear regression assumptions

```{r}
par(mfrow=c(1,3))
plot(resid(taylor.fit2)~fitted(taylor.fit2), xlab='Fitted', ylab='Residuals');abline(h=0,lty=2)
qqnorm(resid(taylor.fit2),ylab='Residuals'); qqline(resid(taylor.fit2),lty=2)
hist(resid(taylor.fit2),main="", xlab="Residuals",col='lightblue')
```

# Results and conclusion

```{r}
summary(taylor.fit2)
```
```{r}
confint(taylor.fit2, level = 0.95)
```

## Summary statistics table

```{r}
taylor_albums_joined |>
  group_by(album_name) |>
  summarise(mean_dance = mean(danceability, na.rm = TRUE), sd_dance = sd(danceability, na.rm = TRUE), mean_user = mean(user_score), mean_critic = mean(metacritic_score)) |>
  arrange(desc(mean_dance)) |>
  rename("Album Name" = album_name, "Mean Danceability" = mean_dance, "Standard dev. Danceability"= sd_dance, "Mean User Score" = mean_user, "Mean Critic Score" = mean_critic) |>
  kable(align = "lcccc", digits = 2)
```

